On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2024-01-04 Manuscript/reply.tex
Clopper Pearson Normal Mu

The text from the Appendix has been moved to the Simulation Study 
section.

@@

If all values in the interval are below 0.95, the results would suggest 
that the method either is providing inaccurate estimation, is underestimating 
the process' variability, or a combination of both. If all values in the 
interval are above .95, the results suggest that the method is overestimating 
the process' variability. \citet{brown2001interval} notes that the Wald-type 
interval has poor coverage as the proportion approaches 0 or 1.

\eds{I don't think this answers the question.  The reviewer is saying that 0.95 
is close to the boundary of 1, so the undercoverage observed intervals
(especially when phi -0.4) may be due, at least in part, to the flaws 
of the asymptotic Wald interval you are using. 
\@ Jun: do you think he should try exact Clopper-Pearson
intervals for at least a few cases of undercoverage to verify it is not the Wald
interval that is causing the undercoverage, then comment on this in at least the
reply (and possibly also in the main paper)?}

>>>>

The text from the Appendix has been moved to the Simulation Study 
section. The second reviewer suggested block size as an additional experimental
factor, so the paragraphs for normal and exponential error structures have
been adjusted accordingly.

@@

Because it is unlikely for the coverage to 
exactly match the nominal level, we can construct a 95\% Wald-type CI of the 
coverage rate 
(which is an estimate of a proportion with $R = 10000$). If the proportion 0.95 
is included in the interval, the block bootstrap method is likely performing 
well. If all values in the interval are below 0.95, the results would suggest 
that the method either is providing inaccurate estimation, is underestimating 
the process' variability, or a combination of both. If all values in the 
interval are above .95, the results suggest that the method is overestimating 
the process' variability. \citet{brown2001interval} notes that the Wald-type 
interval has poor coverage as the proportion approaches 0 or 1.

\eds{I don't think this answers the question.  The reviewer is saying that 0.95 
is close to the boundary of 1, so the undercoverage observed intervals
(especially when phi -0.4) may be due, at least in part, to the flaws 
of the asymptotic Wald interval you are using. 
\@ Jun: do you think he should try exact Clopper-Pearson
intervals for at least a few cases of undercoverage to verify it is not the Wald
interval that is causing the undercoverage, then comment on this in at least the
reply (and possibly also in the main paper)?}
\mc{plot_norm_mu_1_cup.pdf (exact Clopper-Pearson) seems to have about the same 
widths for high 
proportions
(especially for phi = -0.4) as plot_norm_mu_1.pdf (Wald-Type)}
